Fig3

### 2020-02-19 analysis/figure-3.Rmd
working on PRL results
better prl figures

c <- plotfriz(charfviz) + labs(subtitle = "  ")

@@

```{r determinePRLhiglow}
PRLvsd2 <- PRLvsd %>%
  filter(tissue == "pituitary")
head(PRLvsd2)

@@

b <- ggplot(PRLvsd3, aes(x = hiloPRL, y = counts, fill = sex))  +
  geom_boxplot() +
  labs(x = "Prolactin, binned", y = "Prolactin expression")+
  theme_B3() + theme(legend.position = "none") +
  scale_fill_manual(values = sexcolors)

plot_grid(a,b, nrow = 1, rel_widths = c(1,1))

@@

write.csv(PRLvsd,"../results/PRLvsd3.csv", row.names = F)
```

>>>>

c <- plotfriz(charfviz) + labs(subtitle = "  ") +
  ylim(-250000,500000) + xlim(-250000,500000) + 
  theme(axis.text = element_blank())

@@

```{r determinePRLhiglo, fig.height = 6, fig.width=3}
PRLvsd2 <- PRLvsd %>%
  filter(tissue == "pituitary")
head(PRLvsd2)

@@

b <- ggplot(PRLvsd3, aes(x = sex, y = counts, fill = sex, color = hiloPRL))  +
  geom_boxplot() +
  labs(x = "Prolactin, binned into `lo` and `hi`", y = "Prolactin expression")+
  theme_B3() + theme(legend.position = "none") +
  scale_fill_manual(values = allcolors) +
  scale_color_manual(values = allcolors)

plot_grid(a,b, nrow = 2, rel_widths = c(1,1))

@@

write.csv(PRLvsd3,"../results/PRLvsd.csv", row.names = F)
```
